Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2014-07-25 draft.tex
[appendix B-D] \phi -> \theta_3

\section{Application to $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ (S-wave and P-wave)}
\label{app:btokstarll}

The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
The $q^2$-differential decay width reads
\begin{equation}
    \frac{\rmdx{\Gamma}}{\rmdx{q^2}} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions\footnote{%
    We consistently use the label "$i$" to denote angular function and observables that arise
    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
} read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\\
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
\end{aligned}
\end{equation}
We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \phi) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_k(q^2) \equiv J_k(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\

@@

The class of semileptonic $\bar{B}\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P_1$, and $P_2$ are pseudoscalar mesons,
and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
Their decay PDFs can generally be written as \cite{Lee:1992ih}
\begin{equation}
    P(q^2, p^2, \cos\theta_1, \cos \theta_2, \theta_3) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{p^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_k(\cos\theta_1,\phi)\,,
\end{equation}
where
\begin{equation}
\begin{aligned}
    f_1 & = 1\,,              &
    f_2 & = \cos 2\theta_1\,, &
    f_3 & = \sin^2\theta_1 \cos 2\phi\,,\\
    f_4 & = \sin 2\theta_1 \cos  \phi\,,&
    f_5 & = \sin  \theta_1 \cos  \phi\,,&
    f_6 & = \cos  \theta_1\,, \\
    f_7 & = \sin  \theta_1 \sin  \phi\,,&
    f_8 & = \sin 2\theta_1 \sin  \phi\,,&
    f_9 & = \sin^2\theta_1 \sin 2\phi\,.\\
\end{aligned}
\end{equation}
Here we denote dilepton mass squared and the dilepton helicity angle as $q^2$ and $\theta_1$, while
the dimeson mass squared and the dimeson helicity angles are denoted as $p^2$ and $\theta_2$. The
azimuthal angle is denoted as $\theta_3$.
The total decay width is
\begin{equation}
    \langle \Gamma\rangle = \int_0^\pi \rmdx{\theta_2} \rmdx{q^2} \rmdx{p^2} \sin\theta_2 \frac{3I_1(q^2, p^2, \cos\theta_2) - I_2(q^2, p^2, \cos\theta_2)}{3}\,.
\end{equation}
As previous, we transform from a $\cos\theta_2$-dependence to a $\theta_2$-dependence.
\begin{equation}
\begin{aligned}
    P(q^2, p^2, \theta_1, \theta_2, \theta_3)
    & = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \theta_3) \sin\theta_1 \sin\theta_2\\
    & \equiv \frac{1}{4\pi} \sum_k S_k(q^2, p^2, \theta_2) f_k(\theta_1, \theta_3) \sin\theta_1\,.
\end{aligned}
\end{equation}
where we also define $S_k(q^2, p^2, \theta_2) \equiv \sin\theta_2 I_k(q^2, p^2, \cos\theta_2) / \langle \Gamma\rangle$.\\

The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{21 + 15 \cos 2\theta_1}{16}\,, &
    \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
    \hat{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\phi     \,,\\
    \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \phi     \,, &
    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \phi     \,, &
    \hat{f}_6 & = 3 \cos\theta_1                   \,,\\
    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \phi     \,, &
    \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \phi     \,, &
    \hat{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\phi     \,.\\
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\phi} \hat{f}_i(\theta_1,\phi) P(q^2, k^2, \theta_1,\theta_2,\phi) = S_i(q^2, k^2, \theta_2)\,.
\end{equation}

@@

The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts -- reads \cite{Boeer:2014xx}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \phi) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\phi}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \phi)\,,
\end{equation}
where $q^2$ denotes the dilepton mass squared, $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
helicity angles in the dilepton and
$N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
The basis of angular functions reads \cite{Boeer:2014xx}
\begin{equation}
    \begin{aligned}
% 1
        f_{1ss} & = \sin^2\theta_1 &
        f_{1cc} & = \cos^2\theta_1 &
        f_{1c}  & = \cos\theta_1\\
% 2
        f_{2ss} & = \sin^2\theta_1 \cos\theta_2 &
        f_{2cc} & = \cos^2\theta_1 \cos\theta_2 &
        f_{2c}  & = \cos\theta_1   \cos\theta_2 \\
% 3
        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
% 4
        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\theta_3
    \end{aligned}
\end{equation}
The decay width reads
\begin{equation}
    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}
\end{equation}
In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \theta_3) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_i(q^2) \equiv K_i(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\

The dual basis reads
\begin{equation}
    \begin{aligned}
% 1
        \hat f_{1ss} & = \frac{1}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
        \hat f_{1cc} & = \frac{1}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
        \hat f_{1c}  & = \cos\theta_1\\
% 2
        \hat f_{2ss} & = \frac{3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
        \hat f_{2cc} & = \frac{3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
        \hat f_{2c}  & = 3 \cos\theta_1   \cos\theta_2 \\
% 3
        \hat f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\phi &
        \hat f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\phi \\
% 4
        \hat f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\phi &
        \hat f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\phi
    \end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\phi} P(q^2, \theta_1, \theta_2, \phi) \hat{f}_i(\theta_1, \theta_2, \phi) = S_i(q^2)\,.
\end{equation}

>>>>

\section{Application to $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ (S-wave and P-wave)}
\label{app:btokstarll}
The PDF for the decay $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ --- up to and including P-wave contributions --- has been calculated
for the most general basis of dimension-six $b\to s$ operators. It reads, expressed in terms of the angular observables $\lbrace J_i\rbrace$ \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma}/\rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_k \frac{J_{k}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_k(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $\theta_1 \equiv \theta_\ell$ is the dilepton helicity angle, and $\theta_2 \equiv \theta_{K}$ is the $\bar{K}\pi$ helicity angle, and $\theta_3 \equiv \phi$ is the azimuthal angle.
The $q^2$-differential decay width reads
\begin{equation}
    \frac{\rmdx{\Gamma}}{\rmdx{q^2}} = \frac{\big(3 J_{1c} - J_{2c}\big) + 2\big(3J_{1s} - J_{2s}\big)}{3}\,.
\end{equation}
The angular functions\footnote{%
    We consistently use the label "$i$" to denote angular function and observables that arise
    from interference between S-wave and P-wave amplitudes. Our convention is related to the convention
    of \cite{Bobeth:2012vn} through $f_{1i} \leftrightarrow f_{1sc}$, $f_{2i} \leftrightarrow f_{2sc}$.
} read \cite{Blake:2012mb,Bobeth:2012vn}
\begin{equation}
\begin{aligned}
    f_{1s} & = \sin^2\theta_2 &
    f_{1c} & = \cos^2\theta_2 &
    f_{1i} & = \cos\theta_2\\
    f_{2s} & = \sin^2\theta_2 \cos 2\theta_1 &
    f_{2c} & = \cos^2\theta_2 \cos 2\theta_1 &
    f_{2i} & = \cos\theta_2 \cos 2\theta_1\\
    f_{3}  & = \sin^2\theta_2\sin^2\theta_1 \cos 2\theta_3 &
    f_{4}  & = \sin 2\theta_2 \sin 2\theta_1 \cos\theta_3 &
    f_{4i} & = \sin\theta_2 \sin 2\theta_1 \cos\theta_3\\
    f_{5}  & = \sin 2\theta_2 \sin \theta_1 \cos\theta_3 & & &
    f_{5i} & = \sin\theta_2 \sin \theta_1 \cos\theta_3\\
    f_{6s} & = \sin^2\theta_2 \cos\theta_1 &
    f_{6c} & = \cos^2\theta_2 \cos\theta_1\\
    f_{7}  & = \sin 2\theta_2 \sin \theta_1 \sin\theta_3 & & &
    f_{7i} & = \sin\theta_2 \sin \theta_1 \sin\theta_3\\
    f_{8}  & = \sin 2\theta_2 \sin 2\theta_1 \sin\theta_3 & & &
    f_{8i} & = \sin\theta_2 \sin 2\theta_1 \sin\theta_3\\
    f_{9}  & = \sin^2\theta_2\sin^2\theta_1 \sin 2\theta_3\\
\end{aligned}
\end{equation}
We indicate contributions from the interference of S waves and P waves by an index \emph{i}. In terms of the angles $\theta_1$ and $\theta_2$, instead of their cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_k S_k(q^2) f_k(\cos\theta_1, \cos\theta_2, \theta_3) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_k(q^2) \equiv J_k(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\

@@

The class of semileptonic $\bar{B}\to P_1 P_2 \ell_1\bar\ell_2$ decays, where $P_1$, and $P_2$ are pseudoscalar mesons,
and $\ell_1$ and $\bar\ell_2$ are charged or neutral leptons, includes decays
such as $\bar{B}\to\bar{K}\pi\ell^+\ell^-$ and $\bar{B}\to \pi\pi\ell^-\bar\nu_\ell$.
Their decay PDFs can generally be written as \cite{Lee:1992ih}
\begin{equation}
    P(q^2, p^2, \cos\theta_1, \cos \theta_2, \theta_3) = \frac{1}{\langle \Gamma\rangle}\frac{\rmdx{^5 \Gamma}}{\rmdx{q^2} \rmdx{p^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_k(\cos\theta_1,\theta_3)\,,
\end{equation}
where
\begin{equation}
\begin{aligned}
    f_1 & = 1\,,              &
    f_2 & = \cos 2\theta_1\,, &
    f_3 & = \sin^2\theta_1 \cos 2\theta_3\,,\\
    f_4 & = \sin 2\theta_1 \cos  \theta_3\,,&
    f_5 & = \sin  \theta_1 \cos  \theta_3\,,&
    f_6 & = \cos  \theta_1\,, \\
    f_7 & = \sin  \theta_1 \sin  \theta_3\,,&
    f_8 & = \sin 2\theta_1 \sin  \theta_3\,,&
    f_9 & = \sin^2\theta_1 \sin 2\theta_3\,.\\
\end{aligned}
\end{equation}
Here we denote dilepton mass squared and the dilepton helicity angle as $q^2$ and $\theta_1$, while
the dimeson mass squared and the dimeson helicity angles are denoted as $p^2$ and $\theta_2$. The
azimuthal angle is denoted as $\theta_3$.
The total decay width is
\begin{equation}
    \langle \Gamma\rangle = \int_0^\pi \rmdx{\theta_2} \rmdx{q^2} \rmdx{p^2} \sin\theta_2 \frac{3I_1(q^2, p^2, \cos\theta_2) - I_2(q^2, p^2, \cos\theta_2)}{3}\,.
\end{equation}
As previous, we transform from a $\cos\theta_2$-dependence to a $\theta_2$-dependence.
\begin{equation}
\begin{aligned}
    P(q^2, p^2, \theta_1, \theta_2, \theta_3)
    & = \frac{1}{4\pi} \sum_k \frac{I_k(q^2, p^2, \cos\theta_2)}{\Gamma} f_i(\theta_1, \theta_3) \sin\theta_1 \sin\theta_2\\
    & \equiv \frac{1}{4\pi} \sum_k S_k(q^2, p^2, \theta_2) f_k(\theta_1, \theta_3) \sin\theta_1\,.
\end{aligned}
\end{equation}
where we also define $S_k(q^2, p^2, \theta_2) \equiv \sin\theta_2 I_k(q^2, p^2, \cos\theta_2) / \langle \Gamma\rangle$.\\

The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{21 + 15 \cos 2\theta_1}{16}\,, &
    \hat{f}_2 & = \frac{15 + 45 \cos 2\theta_1}{16}\,, &
    \hat{f}_3 & = \frac{15}{4} \sin^2\theta_1 \cos 2\theta_3     \,,\\
    \hat{f}_4 & = \frac{15}{4} \sin 2\theta_1 \cos  \theta_3     \,, &
    \hat{f}_5 & = 3            \sin  \theta_1 \cos  \theta_3     \,, &
    \hat{f}_6 & = 3 \cos\theta_1                   \,,\\
    \hat{f}_7 & = 3            \sin  \theta_1 \sin  \theta_3     \,, &
    \hat{f}_8 & = \frac{15}{4} \sin 2\theta_1 \sin  \theta_3     \,, &
    \hat{f}_9 & = \frac{15}{4} \sin^2\theta_1 \sin 2\theta_3     \,.\\
\end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \int_0^{2\pi} \rmdx{\theta_3} \hat{f}_i(\theta_1,\theta_3) P(q^2, k^2, \theta_1,\theta_2,\theta_3) = S_i(q^2, k^2, \theta_2)\,.
\end{equation}

@@

The PDF for the decay --- in the presence of Standard-Model operators and their chirality-flipped counter parts -- reads \cite{Boeer:2014xx}
\begin{equation}
    P(q^2, \cos\theta_1, \cos\theta_2, \theta_3) = \frac{1}{\rmdx{\Gamma} /\, \rmdx{q^2}} \frac{\rmdx{^4\Gamma}}{\rmdx{q^2} \rmdx{\cos\theta_1} \rmdx{\cos\theta_2} \rmdx{\theta_3}} = \frac{3}{8\pi} \sum_i \frac{K_{i}(q^2)}{\rmdx{\Gamma} /\, \rmdx{q^2}} f_i(\cos\theta_1, \cos\theta_2, \theta_3)\,,
\end{equation}
where $q^2$ denotes the dilepton mass squared, $\theta_1 \equiv \theta_\ell$ and $\theta_2 \equiv \theta_\Lambda$ denote the
helicity angles in the dilepton and
$N\pi$ systems, respectively, and $\theta_3 = \phi$ denotes the azimuthal angle.
The basis of angular functions reads \cite{Boeer:2014xx}
\begin{equation}
    \begin{aligned}
% 1
        f_{1ss} & = \sin^2\theta_1 &
        f_{1cc} & = \cos^2\theta_1 &
        f_{1c}  & = \cos\theta_1\\
% 2
        f_{2ss} & = \sin^2\theta_1 \cos\theta_2 &
        f_{2cc} & = \cos^2\theta_1 \cos\theta_2 &
        f_{2c}  & = \cos\theta_1   \cos\theta_2 \\
% 3
        f_{3sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
        f_{3s}  & = \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
% 4
        f_{4sc} & = \sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
        f_{4s}  & = \sin\theta_1              \sin\theta_2 \sin\theta_3
    \end{aligned}
\end{equation}
The decay width reads
\begin{equation}
    \frac{\rmdx{\Gamma}} {\rmdx{q^2}} = 2 K_{1ss} + K_{1cc}
\end{equation}
In terms of the angles $\theta_1$ and $\theta_2$, instead of the cosines, the PDF reads
\begin{equation}
    P(q^2, \theta_1, \theta_2, \theta_3) = \frac{3}{8\pi} \sum_i S_i(q^2) f_i(\cos\theta_1, \cos\theta_2, \theta_3) \sin\theta_1 \sin\theta_2\,,
\end{equation}
where we also define $S_i(q^2) \equiv K_i(q^2) / (\rmdx{\Gamma} /\, \rmdx{q^2})$.\\

The dual basis reads
\begin{equation}
    \begin{aligned}
% 1
        \hat f_{1ss} & = \frac{1}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) &
        \hat f_{1cc} & = \frac{1}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) &
        \hat f_{1c}  & = \cos\theta_1\\
% 2
        \hat f_{2ss} & = \frac{3}{4}\big(3 \sin^2\theta_1 - 2 \cos^2\theta_1\big) \cos\theta_2 &
        \hat f_{2cc} & = \frac{3}{2}\big(- \sin^2\theta_1 + 4 \cos^2\theta_1\big) \cos\theta_2 &
        \hat f_{2c}  & = 3 \cos\theta_1   \cos\theta_2 \\
% 3
        \hat f_{3sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \cos\theta_3 &
        \hat f_{3s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \cos\theta_3 \\
% 4
        \hat f_{4sc} & = \frac{15}{2}\sin\theta_1 \cos\theta_1 \sin\theta_2 \sin\theta_3 &
        \hat f_{4s}  & = \frac{3}{2} \sin\theta_1              \sin\theta_2 \sin\theta_3
    \end{aligned}
\end{equation}
such that
\begin{equation}
    \int_0^\pi \rmdx{\theta_1} \int_0^\pi \rmdx{\theta_2} \int_0^{2\pi} \rmdx{\theta_3} P(q^2, \theta_1, \theta_2, \theta_3) \hat{f}_i(\theta_1, \theta_2, \theta_3) = S_i(q^2)\,.
\end{equation}
